### 2024-04-20 docs/SOSP 2024/results.tex
Fix typos

\begin{figure*}[htb]
  \begin{subfigure}[t]{.32\linewidth}
    \includegraphics[width=\textwidth]{figures/geomean_speedup_4060_kernel_time_total_time.png}
    \caption{\label{Fig:TBvsRAPIDSTahoe_4060_Speedup}Speedup vs batch size.}      
  \end{subfigure}
  \begin{subfigure}[t]{.32\linewidth}
    \includegraphics[width=\textwidth]{figures/speedup_bar_graph_1024.png}
    \caption{\label{Fig:KernelTimeIndividualBenchmarks4060a} Batch size 1024.}
  \end{subfigure}
  \begin{subfigure}[t]{.32\linewidth}
    \includegraphics[width=\textwidth]{figures/speedup_bar_graph_8192.png}
    \caption{\label{Fig:KernelTimeIndividualBenchmarks4060b} Batch size 8192.}
  \end{subfigure}
  % \hfill
  \caption{The first graph shows kernel and total time speedup of \Treebeard{} over RAPIDS and Tahoe (geomean over real-world 
  benchmarks) across batch sizes on NVIDIA RTX 4060. The bar graphs shows the kernel time speedup of \Treebeard{} per benchmark. Numbers on the bars are inference times per sample in $\mu$s for RAPIDS and Tahoe.}
\end{figure*}

@@

\subsubsection*{Real-world models}
Figure~\ref{Fig:TBvsRAPIDSTahoe_4060_Speedup} shows the geomean speedup of \Treebeard{} over RAPIDS and Tahoe at different batch sizes on RTX 4060. 
We do not show results for XGBoost since the kernel time speedups are an order of magnitude higher ($9\times$---$40\times$) and too large to fit on the same graph.  
The plot has lines for kernel time and total time speedup over RAPIDS and kernel time speedup over Tahoe. As can been seen 
\Treebeard{} is uniformly faster than Tahoe{\footnote{Tahoe does not support multiclass models. To enable comparison, we ran 
the multiclass models (\op{covtype} and \op{letters}) as regression models only with Tahoe. We also noticed that some variants
of Tahoe produce wrong results (as reported by its own tests) for \op{letters} and \op{year}. In these cases, we pick the 
time of the fastest variant that gives the correct results.}} by $2-2.5\times$ at all batch sizes. 
Compared to RAPIDS, \Treebeard{} is about $4\times$ faster at batch size 512. The relative performance of RAPIDS improves 
with batch size from 512---4096 as RAPIDS is optimized for larger batches. \Treebeard{} is still consistently faster by $1.5-2\times$ all the way up to a very large batch size of $16k$. 
The plot also shows that the speedups are significant even when the overhead of data transfer to and from the GPU
is included. They are lower than kernel time speedup as both systems have a constant additional transfer overhead.

@@

Figures~\ref{Fig:KernelTimeIndividualBenchmarks4060a} and ~\ref{Fig:KernelTimeIndividualBenchmarks4060b} 
show per benchmark results at two different batch sizes. 
\Treebeard{} is able to find better schedules than both RAPIDS and Tahoe on each of the benchmarks. It consistently
outperforms both systems, achieving a speedup of upto $12\times$.
For about half the benchmarks, the speedup is $2\times$ or more over both baselines at batch size 8192.
% \begin{comment}
\subsubsection*{Synthetic models}
To establish that \Treebeard{} can consistently find betters schedules, we performed an exhaustive comparison between \Treebeard{} and RAPIDS on the 700 randomly generated models.   
Figure~\ref{fig:randomModels4060} the results at batch sizes 512 and 4096 on all models, on RTX 4060. 
Each plot shows the speedup of \Treebeard{} over RAPIDS along the z-axis, with the x-axis and y-axis representing the number of trees and the number of features. 
While the exact trends at different batch sizes vary it can be seen that \Treebeard{} consistently outperforms RAPIDS by $1.5-8\times$. Along the tree 
dimension we find that the speedup is very high with fewer trees and stabilizes at around $2\times$ from 300 onwards. We note that \Treebeard{} continues to scale well 
when the number of trees are increased even further. It achieves a speedup of around $2\times$ compared to RAPIDS on \op{letters}, a real-world benchmark
with 26K trees.

@@

\subsubsection*{Schedule Sensitivity Across GPUs}
We designed additional experiments to evaluate whether the best schedule (as picked by the heuristic) from one GPU can be used on another.
Figure \ref{Fig:AutotuningSpeedupvs4060Sched} reports the Geomean performance improvements of using the best schedule on T400 and MI210 compared to using the best schedule found on the RTX 4060 (for a given batch size).
As can be seen the T400 specific schedule is 1.05$\times$ to 1.2$\times$ better 
with the maximum difference being $2\times$ (\op{epsilon} at batch size 512).
There is a much larger variation in performance on MI120. For example, 
the geomean speedup over all benchmarks is 1.5$\times$ at batch size 16k (maximum 2$\times$ for the \op{letters} benchmark).
In conclusion, schedules found on one GPU do not carry over to other GPUs and often result in sub-optimal performance.
It is necessary tune schedules on each target to achieve the best performance.

@@

\subsection{Additional Observations}
%Beyond portable performance, our evaluation indicates that \Treebeard{} has several additional advantages over existing systems.
\subsubsection*{Cost Performance trade-off Across Hardware Platforms}
Two of the three GPU targets we use are commodity GPUs that cost less than \$400. They 
are in fact much cheaper than the CPU we evaluate on. Despite this, performance on GPUs
is significantly better than on CPUs (by an order of magnitude on RTX 4060).
\Treebeard{} can therefore help data scientists make the best use of 
available processors on their systems.

\subsubsection*{A Note on batch size}
Batch size, exposes a trade-off between latency and throughput. It is not possible to use 
large batch sizes in latency sensitive applications. 
Ideally, one would like 
to maximize performance while respecting the batch size constraint imposed 
by the application. \Treebeard{} enables users to explore this trade-off.  
%\subsection*{}
\bigbreak
\noindent
Overall, our evaluation shows that \Treebeard{} is able to efficiently generate 
high-performance code for processors ranging from NVIDIA and AMD GPUs to Intel CPUs.
On all platforms and models that we tested on, \Treebeard{} significantly outperforms
state-of-the-art systems like RAPIDS, Tahoe, XGBoost and \TreebeardOLD{}.

>>>>

\begin{figure*}[htb]
  \begin{subfigure}[t]{.32\linewidth}
    \includegraphics[width=\textwidth]{figures/geomean_speedup_4060_kernel_time_total_time.png}
    \caption{\label{Fig:TBvsRAPIDSTahoe_4060_Speedup}Speedup vs batch size.}      
  \end{subfigure}
  \begin{subfigure}[t]{.32\linewidth}
    \includegraphics[width=\textwidth]{figures/speedup_bar_graph_1024.png}
    \caption{\label{Fig:KernelTimeIndividualBenchmarks4060a} Batch size 1024.}
  \end{subfigure}
  \begin{subfigure}[t]{.32\linewidth}
    \includegraphics[width=\textwidth]{figures/speedup_bar_graph_8192.png}
    \caption{\label{Fig:KernelTimeIndividualBenchmarks4060b} Batch size 8192.}
  \end{subfigure}
  % \hfill
  \caption{The first graph shows kernel and total time speedup of \Treebeard{} over RAPIDS and Tahoe (geomean over real-world 
  benchmarks) across batch sizes on NVIDIA RTX 4060. The bar graphs show the kernel time speedup of \Treebeard{} per benchmark. Numbers on the bars are inference times per sample in $\mu$s for RAPIDS and Tahoe.}
\end{figure*}

@@

\subsubsection*{Real-world Models}
Figure~\ref{Fig:TBvsRAPIDSTahoe_4060_Speedup} shows the geomean speedup of \Treebeard{} over RAPIDS and Tahoe at different batch sizes on RTX 4060. 
We do not show results for XGBoost since the kernel time speedups are an order of magnitude higher ($9\times$---$40\times$) and too large to fit on the same graph.  
The plot has lines for kernel time and total time speedup over RAPIDS and kernel time speedup over Tahoe. As can been seen 
\Treebeard{} is uniformly faster than Tahoe{\footnote{Tahoe does not support multiclass models. To enable comparison, we ran 
the multiclass models (\op{covtype} and \op{letters}) as regression models only with Tahoe. We also noticed that some variants
of Tahoe produce wrong results (as reported by its own tests) for \op{letters} and \op{year}. In these cases, we pick the 
time of the fastest variant that gives the correct results.}} by $2-2.5\times$ at all batch sizes. 
Compared to RAPIDS, \Treebeard{} is about $4\times$ faster at batch size 512. The relative performance of RAPIDS improves 
with batch size from 512---4096 as RAPIDS is optimized for larger batches. \Treebeard{} is still consistently faster by $1.5-2\times$ all the way up to a very large batch size of $16k$. 
The plot also shows that the speedups are significant even when the overhead of data transfer to and from the GPU
is included. They are lower than kernel time speedup as both systems have a constant additional transfer overhead.

@@

Figures~\ref{Fig:KernelTimeIndividualBenchmarks4060a} and ~\ref{Fig:KernelTimeIndividualBenchmarks4060b} 
show per benchmark results at two different batch sizes. 
\Treebeard{} is able to find better schedules than both RAPIDS and Tahoe on each of the benchmarks. It consistently
outperforms both systems, achieving a speedup of upto $12\times$.
For about half the benchmarks, the speedup is $2\times$ or more over both baselines at batch size 8192.
% \begin{comment}
\subsubsection*{Synthetic Models}
To establish that \Treebeard{} can consistently find betters schedules, we performed an exhaustive comparison between \Treebeard{} and RAPIDS on the 700 randomly generated models.   
Figure~\ref{fig:randomModels4060} the results at batch sizes 512 and 4096 on all models, on RTX 4060. 
Each plot shows the speedup of \Treebeard{} over RAPIDS along the z-axis, with the x-axis and y-axis representing the number of trees and the number of features. 
While the exact trends at different batch sizes vary it can be seen that \Treebeard{} consistently outperforms RAPIDS by $1.5-8\times$. Along the tree 
dimension we find that the speedup is very high with fewer trees and stabilizes at around $2\times$ from 300 onwards. We note that \Treebeard{} continues to scale well 
when the number of trees are increased even further. It achieves a speedup of around $2\times$ compared to RAPIDS on \op{letters}, a real-world benchmark
with 26K trees.

@@

\subsubsection*{Schedule Sensitivity Across GPUs}
We designed additional experiments to evaluate whether the best schedule (as picked by the heuristic) from one GPU can be used on another.
Figure \ref{Fig:AutotuningSpeedupvs4060Sched} reports the geomean performance improvements of using the best schedule on T400 and MI210 compared to using the best schedule found on the RTX 4060 (for a given batch size).
As can be seen the T400 specific schedule is 1.05$\times$ to 1.2$\times$ better 
with the maximum difference being $2\times$ (\op{epsilon} at batch size 512).
There is a much larger variation in performance on MI120. For example, 
the geomean speedup over all benchmarks is 1.5$\times$ at batch size 16k (maximum 2$\times$ for the \op{letters} benchmark).
In conclusion, schedules found on one GPU do not carry over to other GPUs and often result in sub-optimal performance.
It is necessary to tune schedules on each target to achieve the best performance.

@@

\subsection{Additional Observations}
%Beyond portable performance, our evaluation indicates that \Treebeard{} has several additional advantages over existing systems.
\subsubsection*{Cost Performance Trade-off Across Hardware Platforms}
Two of the three GPU targets we use are commodity GPUs that cost less than \$400. They 
are in fact much cheaper than the CPU we evaluate on. Despite this, performance on GPUs
is significantly better than on CPUs (by an order of magnitude on RTX 4060).
\Treebeard{} can therefore help data scientists make the best use of 
available processors on their systems.

\subsubsection*{A Note on Batch Size}
Batch size, exposes a trade-off between latency and throughput. It is not possible to use 
large batch sizes in latency sensitive applications. 
Ideally, one would like 
to maximize performance while respecting the batch size constraint imposed 
by the application. \Treebeard{} enables users to explore this trade-off.  
%\subsection*{}
\bigbreak
\noindent
Overall, our evaluation shows that \Treebeard{} is able to efficiently generate 
high-performance code for processors ranging from NVIDIA and AMD GPUs to Intel CPUs.
On all platforms and models that we tested on, \Treebeard{} significantly outperforms
state-of-the-art systems like RAPIDS, Tahoe, XGBoost and \TreebeardOLD{}.
